%-------------------------
% Resume in Latex
% Author : Vaishanth
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}%\setmainfont{Times New Roman}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}

\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% \usepackage[T1]{fontenc}
% \usepackage[T1]{fontenc}
% \usepackage{cochineal}
% \usepackage{fourier}

% \usepackage{fontspec}
% \usepackage{polyglossia}
% \setmainlanguage{german}
% \setmainfont{Times New Roman}

% serif
\usepackage{CormorantGaramond}
\usepackage{charter}

% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
\urlstyle{same}

\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSingleSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.1in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------\usepackage{fontspec}
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%----------HEADING----------


\begin{center}
    {\huge Abhishek Bhattacharjee} \\ \vspace{2pt} 
    {+91 9004666967} ~ 
    \small{-}
    \href{[https://abhishek-tech.com/]}{\color{blue}{Portfolio}} ~ 
    \small{-}
    \href{mailto:[abhishek.bh777@gmail.com]}{\color{blue}{abhishek.bh777@gmail.com}} ~ 
    \small{-}
    \href{[https://www.linkedin.com/in/abhib7/]}{ \color{blue}{linkedin.com/in/abhib7}}  ~
    \small{-}
    \href{[https://github.com/AbhiB7]}{ \color{blue}{github.com/AbhiB7}} ~
    \vspace{-7pt}
\end{center}

%-----------EDUCATION-----------
\section{\color{airforceblue}EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Fr. Conceicao Rodrigues College of Engineering, Mumbai University}{Mumbai,Maharashtra}
      {Bachelor of Engineering, Electronics and Computer Science. CGPA:8.48}{2019-2023}
    \vspace{-4pt}
     \resumeSubheading
      {Fr. Agnel Multipurpose School and Jr College}{Navi-Mumbai,Maharashtra}
      {Higher Secondary School Certificate, Percentage: 80.46\%}{2018-19}
 \resumeSubheading
      {Fr. Agnel Multipurpose School and Jr College}{Navi-Mumbai,Maharashtra}
      {Secondary School Certificate, Percentage: 90.20\%}{2016-17}
  \resumeSubHeadingListEnd
  \vspace{-10pt}


 
 %-----------EXPERIENCE-----------
\section{\color{airforceblue}WORK EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data Science Intern}{} 
      {Cyient Limited, Hyderabad, Telangana (Hybrid)}{Jul 2023 – Oct 2023}
      \resumeItemListStart
            \resumeItem{\normalsize{ Analysed prognostics data from train systems for data cleaning, data visualization and outlier detection.}}
      \resumeItemListEnd  
  \resumeSubHeadingListEnd
\vspace{-12pt}



 %-----------PROJECTS-----------
\section{\color{airforceblue}PROJECTS}    
    \resumeItemListStart
        \vspace{0.5pt}
        \resumeItem{\normalsize{\textbf{Natural Disaster Identification and Representation on a Map | Final Year Project \href{https://github.com/AbhiB7/Natural-Disaster-Identificaiton-And-Representaiton-On-a-Map}{\color{blue}\underline{GitHub}} \href{https://www.youtube.com/watch?v=OS9cMOwmd1M}{\color{blue}\underline{YouTube}}} }\\
      Worked with the BERT model to identify natural disaster tweets, fetched from the former twitter API. Used CUDA technology in TensorFlow to significantly shorten training times.
   } 
        \vspace{-5pt}
        
        \resumeItem{\normalsize{\textbf{YouTube Comment Sentiment Analysis | Mini Project Third Year \href{https://github.com/AbhiB7/Yt-Comment-Sentiment-Analysis}{\color{blue}\underline{GitHub}} \href{https://www.youtube.com/watch?v=0-SvC4Br2dM}{\color{blue}\underline{YouTube}}}\\
Scraped YouTube comment section of a video and displayed a word map to show the sentiments of that video. Classified comments using naïve bayes using tools like NLTK and Sci-kit learn.} }
        \vspace{-5pt}

\resumeItem{\normalsize{\textbf{Neovim Configurations written in Lua | Side Project \href{https://github.com/AbhiB7/nvim-config.lua}{\color{blue}\underline{GitHub}}}\\
Turned a simple text editor like Neovim, a derivative of vim into a fully functional IDE. Lua scripting language is used instead of vim script giving an increase in performance.} }
        \vspace{-5pt}

 \resumeItem{\normalsize{\textbf{Personal Finance Website | Mini Project Second Year \href{https://github.com/AbhiB7/Personal-Finance-Webapp}{\color{blue}\underline{GitHub}}}\\
 Built a simple personal finance website using the LAMP stack, especially PHP and MYSQL for database.} }
        \vspace{-5pt}

\resumeItem{\normalsize{\textbf{Web Scraping of E-commerce Websites for Innovative Technologies| Side Project }\\
Used Python scrapping tools like Beautiful Soup and Selenium to scrape websites for product information.} }
        \vspace{-5pt}

        % copy and paste above resumeItem block to add more 
       
    \resumeItemListEnd     
 \vspace{-12pt}
%
%-----------EXTRACURRICULAR---------------
\section{\color{airforceblue}Certification}
    
      \resumeItemListStart
        \resumeItem{\normalsize{\textbf{NLP - Natural Language Processing with Python \href{https://www.udemy.com/certificate/UC-b9b6ce50-fa0b-4930-a995-0739631a2760/}{\color{blue}\underline{Certificate}}}  \\Skills: Natural Language Processing, Data Manipulation, Machine Learning, Python }} 
        \vspace{-5pt}
        
          \resumeItem{\normalsize{\textbf{IBM - What is Data Science? \href{https://www.coursera.org/account/accomplishments/verify/WQUPAND9DNKW}{\color{blue}\underline{Certificate}}}  \\Skills: Data Science, Data Analysis, Data Visualization}} 
        \vspace{-5pt}

        % copy and paste above resumeItem block to add more 
      \resumeItemListEnd 
      
\vspace{-12pt}
%-----------PROGRAMMING SKILLS-----------
\section{\color{airforceblue}TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{\normalsize{Programming Languages:}}{ \normalsize{Python, C, C++, SQL, Lua, HTML, CSS, PHP, JavaScript, Bash}} \\
      \vspace{1.2pt}
      
     \textbf{\normalsize{Libraries and Tools:}}{ \normalsize{NLTK, NumPy, Matplotlib, Pandas, Requests, BS4, Selenium, Git, Linux}} \\
      \vspace{1.2pt}
      
     \textbf{\normalsize{Technical Skills:}}{ \normalsize{ Natural Language Processing, Web Scraping and Crawling, Data Manipulation and Analysis}}
\textbf{\normalsize{Language:}}{ \normalsize{ English, Hindi, Marathi}}

     % copy and paste above textbf block to add more 
     }}
 \end{itemize}
 \vspace{-16pt}

\end{document}